---
title: "Monte Carlo"
author: "Nicolas Ayala"
date: "01-10-2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
**Monte Carlo Simulation**
A simulation of insulin consumption is performed for patients diagnosed with diabetes mellitus who are insulin resistant. Based on this scenario, the mean daily insulin expenditure is 1,000 doses and its standard deviation is 250 doses, according to historical data from the Pharmacy Warehouse and the Pharmacy Unit.
```{r}
# Creation of the simulation. The "n" of the experiment is defined and fixed with set.seed.
set.seed(10)
stock_insulin = rnorm (n= 100 , mean= 1000 , sd= 250)
par (mfrow= c(3,1))
plot (stock_insulin, ylab = "Dose", xlab= "Days", main="Daily insulin consumption in the Pharmacy Unit", col="magenta")
hist (stock_insulin, ylab= "Frequency" , xlab= "Dose of Insulin", main= "Absolute distribution of insulin dose per day", col="skyblue1")
hist (stock_insulin, freq = FALSE, main = "Histogram and density curve",xlab= "Dose of Insulin", col="skyblue1")
curve(dnorm (x, mean= 1000 , sd= 250), from= 0 , to= 1500, add= TRUE, col= "magenta", lwd=2)
```


```{r}
cat ("The mean of the measurement for a series of 100 days is:", mean(stock_insulin))
```
```{r}
cat ("The standar desviation for a series of 100 days is:" , sd(stock_insulin))
```


```{r}
# The data mean is 965.8 doses and its standard deviation is 235.3 doses. The results are similar to historical data but not exactly 1,000 and 250, respectively. By replicating "n" events, results closer to the theoretical values could be obtained.
```


```{r}
#If we wanted to study the behavior of insulin consumption in a series of data measured longitudinally, we would have the following representation with a replicate (2). We will focus particularly on the prediction and study of the mean.
set.seed(10)
norm.rep2 = replicate(n= 2, rnorm(n= 100, mean= 1000 , sd= 250))
ts.plot(norm.rep2, main= "Distribution of insulin consumption in a longitudinal series" , ylab= "Dose of Insulin", xlab= "Time series of measurements", col="magenta")
```

Calculation of the theoretical standard error
```{r}
250/ sqrt(1000) # Calculation of the theoretical standard error
```

Standard error of the mean in the problem
```{r}
sd(norm.rep2)
# The standard deviation is 238.32 and the theoretical value of the data series is 238.


sd(apply(X=norm.rep2, MARGIN= 2 , FUN= mean))
# The result of the standard error is 7.35 and the theoretical value is 7.35. The result of the standard deviation is 238.32 and the theoretical value is 250. This is an advance since it improves the amount of data, but nevertheless it would be interesting to know how the error of the measurement of daily insulin consumption behaves in a larger sample. .
```


```{r}
# A replication of the experiment of 50 is made to study how the mean behaves versus the theoretical value.
set.seed(100)
norm.rep50 = replicate(n= 50, rnorm(n= 100, mean= 1000 , sd= 250))
sd(apply(X=norm.rep50, MARGIN= 2 , FUN= mean)) # Mean scatter
```


```{r}
hist(apply(X=norm.rep50, MARGIN= 2 , FUN= mean), 
      main = "Sampling distribution simulation",
      xlab= "Estimation of insulin consumption", ylab= "Absolute frecuency",
      col= 2)

abline(v=mean(norm.rep50), lwd=4, lty=3, col="darkblue")
```

```{r}
cat ("The mean of the measurement for a series of 100 data in an experiment of 2000 replicates is:", mean(norm.rep50))
```


```{r}
cat ("The standard deviation for a series of 100 data in an experiment of 2000 replicates is:" , sd(norm.rep50))
```

Conclusiones
```{r}
# When a Monte Carlo statistical model is applied, the figures resemble the theoretical values when the replications of the events increase, as observed in the replica of 50 where the value of the theoretical mean and the mean of the experiment are very similar. The same happens with the standard deviation, which improves markedly with increasing replicas. This is interesting because it allows the Pharmacy Unit to adequately manage the insulin treatment schedule for patients with diabetes such as those in the data set that has been studied.
```
